---
title: "Asia example"
author: "Rachel Wilkerson"
date: "3 May 2019"
output:
  github_document: default
  html_notebook: default
---
## Prequential diagnostic monitors for Bayesian Networks

Package exists to check the goodness of fit for a BN model. Package is designed to interface with objects of class bnlearn. 

```{r,warning=FALSE, echo=FALSE,message=FALSE}
library(tidyverse)
library(gRain)
library(bnlearn)
library(DiagrammeR)
library(rlang)
library(RColorBrewer)
load(file = "asia_ex.Rdata")

```


```{r, eval=FALSE, message=FALSE}
devtools::install_github('bnmonitoR','rachwhatsit')
```

Load the package from github.
```{r, message=FALSE}
library(bnmonitoR)
```

We will examine the dataset from the bnlearn package from Lauritzen. Details of the variables (nodes) can be found in the documentation for bnlearn.
```{r asia, message=FALSE}
data(asia)
summary(asia)
```

We will specify the structure of the model here. This corresponds to the candidate model from Cowell et al. pg 240
```{r,message=TRUE,cache=TRUE,screenshot.force = TRUE}
asia.dag = model2network("[A][S][T|A][L|S][B|S][D|B:E][E|T:L][X|E]") #this is the candidate model from pg 240
bnlearn::graphviz.plot(asia.dag)
```

### Global monitor

The global monitor is equivalent to the Bayes Factor and offers a good assessment of the model as a whole.
```{r,cache=TRUE,screenshot.force = TRUE}
global.monitor.tbl(asia.dag, alpha = 2, df=asia)
```

The darker colors correspond to nodes with a greater contribution to the Bayes Factor. 
```{r, cache=TRUE}
global.monitor.graph(asia.dag, alpha = 2, df=asia)
```
 
The global monitor is most useful when comparing between models. For instance, following the example from Cowell 1994, Model 0 compares to Model 1 above. Model 0 below has an addition link between smoking and dyspnoea. The effect of this can be seen in the slightly higher contribution of the Bayes factor to node D. This does not have a significant effect on the model as a whole.

```{r}
asia.dag.model0 = model2network("[A][S][T|A][L|S][B|S][E|T:L][X|E][D|B:E:S]") #this is the candidate model from pg 240
model0 <- global.monitor.tbl(asia.dag.model0, alpha = 2, df=asia)
model1 <- global.monitor.tbl(asia.dag, alpha = 2, df=asia)

sum(model0$node.scores)/sum(model1$node.scores)#Bayes Factor
```

```{r, cache=TRUE,screenshot.force = TRUE}
global.monitor.tbl(asia.dag.model0, alpha = 2, df=asia)
global.monitor.graph(asia.dag.model0, alpha = 2, df=asia)

```

### Parent child monitor

This function computes the predictive probabilities for observing the particular combinations of parent and child values.
```{r,screenshot.force = TRUE}
seq.pa.ch.monitor(df=asia, dag=asia.dag, node.name="E", pa.names = c("T","L"), pa.val = c('yes', 'no'),which.val=1)
```

### Node monitors

Two types of node monitors are calculated: marginal and conditional.
```{r}
node.monitor.tbl(asia.dag,asia)
```

```{r,screenshot.force = TRUE}
marg.node.monitor.graph(asia.dag,asia)
```

From this plot, we see that the overall incidence for Smoking, Bronchitis, and Dysnopea are poorly modelled. 
Because there is very little difference between the marginal and conditional nodes, the graphs in this example are virtually indistinguishable.

