---
title: "Asia example"
author: "Rachel Wilkerson"
date: "3 May 2019"
output:
  html_document:
    keep_md: true
---
## Prequential diagnostic monitors for Bayesian Networks

Package exists to check the goodness of fit for a BN model. Package is designed to interface with objects of class bnlearn. 

```{r,warning=FALSE, echo=FALSE,message=FALSE}
library(tidyverse)
library(gRain)
library(bnlearn)
library(DiagrammeR)
library(rlang)
library(RColorBrewer)
load(file = "asia_ex.Rdata")
```


```{r, eval=FALSE, message=FALSE}
devtools::install_github('bnmonitoR','rachwhatsit')
```

Load the package from github.
```{r, message=FALSE}
library(bnmonitoR)
```

We will examine the dataset from the bnlearn package from Lauritzen. Details of the variables (nodes) can be found in the documentation for bnlearn.
```{r asia, message=FALSE}
data(asia)
summary(asia)
```

We will specify the structure of the model here. This corresponds to the candidate model from Cowell et al. pg 240
```{r,message=FALSE,cache=TRUE}
asia.dag = model2network("[A][S][T|A][L|S][B|S][D|B:E][E|T:L][X|E]") #this is the candidate model from pg 240
bnlearn::graphviz.plot(asia.dag)
```

### Global monitor

The global monitor is equivalent to the Bayes Factor and offers a good assessment of the model as a whole.
```{r,cache=TRUE}
global.monitor.tbl(asia.dag, alpha = 2, df=asia)
```

The darker colors correspond to nodes with a greater contribution to the Bayes Factor. 
```{r, cache=TRUE}
global.monitor.graph(asia.dag, alpha = 2, df=asia)
```
 
```{r, cache=TRUE}
asia.dag.model0 = model2network("[A][S][T|A][L|S][B|S][E|T:L][X|E][D|B:E:S]") #this is the candidate model from pg 240
global.monitor.tbl(asia.dag.model0, alpha = 2, df=asia)
global.monitor.graph(asia.dag.model0, alpha = 2, df=asia)

```

### Parent child monitor

This function computes the predictive probabilitie for observing the particular 
```{r}
seq.pa.ch.monitor(df=asia, dag=asia.dag, node.name="T", pa.names = "A", pa.val = 'yes',which.val=2)#why is this so different for learning and no learning??
```

### Node monitors
```{r}
node.monitor.tbl(asia.dag,asia)
```

```{r}
marg.node.monitor.graph(asia.dag,asia)
```

cond.node.monitor.graph(asia.dag,asia)

